Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-14 doc/main_jfm.tex
incorporated fig6(b)
rearrangements

@@

\subsection{Self-Assembly and Relaxation}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure1_Wrapper.pdf}
%\includegraphics[height=2in]{relax2.eps}
%\includegraphics[height=2in]{relax.eps}\\
%\includegraphics[height=2.in]{N58_0pres.pdf}
%\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
\caption{\label{figure2} A JP Vesicle relaxing under a quiescent flow.
  (a) The blue dashed and solid curves are mean magnitudes of the
  particle velocities in $x$ and $y$ directions, respectively. The red
  curve shows the decreasing trend of the mean magnitude of particle
  orientation change. The black dashed line shows the reference of how
  all magnitudes decay. (b) Bilayer configurations for $t=0$ (black) and
  $t=1000$ (red) with particle directors. (c)--(d) show the fluid
  pressure profiles for $t=0$ and $t=1000$ where the background curves
  indicate the streamlines. In panel (c), the pressure value in internal
  fluid is much higher than the pressure outside of the bilayer. After
  the JP vesicle relaxes, this immersed permeable bilayer approaches the
  steady state shown in panel (d).}
\end{figure}

@@

\subsection{Permeability}
Figures~\ref{figure2}c and~\ref{figure2}d demonstrate that the initial, non-equilibrium configuration has a large internal fluid pressure
that vanishes as the configuration tends toward the equilibrium state.  
This suggests that the initial collection of JP is under tension and
this tension is relaxed as fluid is expelled through the inter-particle
spacing. To make a comparison with membrane continuum mechanics, lipid
bilayer membranes have a large area modulus $K_A$ of about $240$ pN
nm$^{-1}$ \cite{NAGLE} and changes in surface area give rise to a
membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
membrane surface area and $A_0$ is the reference surface area in the
non-tensed state. In the two-dimensional vesicles, the tension becomes
\begin{align}
\label{eq:stretch}
\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
\end{align}
where $L$ and $L_0$ are the vesicle arc length and resting length,
respectively. A stretched, circular vesicles has a Laplace pressure 
\begin{align}
\label{eq:LaplacePressure}
\Delta p = \frac{\tilde \gamma}{R},
\end{align}
where $\Delta p$ is the difference in internal pressure to the pressure
at infinity and $R$ is the radius of the circular vesicle. The factor
$R^{-1}$ is the total curvature since the principle curvature in the
direction of the cylinder is zero.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tank-Treading Vesicles}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
Our hydrodynamic simulation studies begin by studying the dynamics of a single JP vesicle suspended in
the shear flow
\begin{align}
  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
\end{align}
with shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
and $\mathbf{e}_y$ for the horizontal and vertical directions,
respectively. It is well known that a vesicle has tank-treading behavior
when there is no viscosity contrast between the fluids inside and
outside of the vesicle.
%Within the framework of the simulation setup,
%the proposed model provides a feature that the fluid viscosity is
%constant over the computational domain and it is capable of performing
%these simulations.

\begin{figure}
\centering
\includegraphics[width=11.5cm]{Figure3_Wrapper.pdf}
%\includegraphics[width=0.3\textwidth]{N58_0.pdf}
%\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
%\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
%\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{\label{figure3} A JP vesicle suspended in a shear flow with
  shear rate $\chi=0.0025$. (a) The initial configuration of a 58-body
  JP vesicle where the black arrows point in the direction of the
  hydrophobic side of the JP. (b) The particle velocities and
  streamlines of the configuration in (a). The streamlines are plotted
  in the background as solid curves and the red arrows represent the
  particle velocities. (c) The deformed tank-treading JP vesicle at
  $t=4000$. (d) The particle velocities and streamlines of the
  configuration in (c). The background colors in panels (a) and (c)
  represent the strength of the hydrophobic attraction potential. The
  blue regions have the weakest action and the red regions in the
  bilayer have the strongest action.}
\end{figure}
%

\begin{figure}
\begin{center}
\includegraphics[width=13.5cm]{Figure4_Wrapper.pdf}
%\hspace{-0.6cm}
%\includegraphics[height=2in]{ReducedArea.pdf}
%\hspace{0.6cm}
%\includegraphics[height=2in]{DecayRate.eps}\\
%\includegraphics[height=2in]{ArcLength.pdf}
%\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{\label{figure4} (a) The reduced area transitioning over time
  for four different shear rates. The smooth curves are a best-fit
  exponential curve. (b) The decay rate $k$, using the exponential fit
  to the data in panel (a), for a number of shear rates. The inset shows
  the terminal reduced areas. (c) The total arc lengths of the midplanes
  over time for four shear rates. (d) The excess length of the
  midplanes. For all panels, a set of shear rates
  $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. The
  legend in panel (d) applies to both panels (a) and (c).}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Inter-Monolayer Friction}
The granulated JP vesicle allows us to consider inter-monolayer slip
between the two leaflets. When the shear rate is sufficiently large,
take $\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip
between a pair of particles over time. The pair we consider are colored
in blue and yellow. In this series of tests, we compute the mean
particle position and mean angle $\theta(t)$ between the particle
relative positions with respect to the vesicle center. It is clear that
the outer leaflet has larger tangential velocity than the inner leaflet
since $\theta(t)$ increases. This inter-leaflet sliding phenomenon is
consistent with what has been seen in articles in molecular dynamics
simulations. (\cite{Zgorski2019,denOtter2007})

\begin{figure}
\begin{center}
\includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} The schematic of the intermonolayer slip over
  time. Taking a shear rate $\chi=0.005$ as an example, we denote the
  mean angle between each particle pair $\theta(t)$ where the angle is
  calculated from the relative position of the particles with respect to
  the JP vesicle's center of mass. The configuration plots have two
  fixed particles marked in yellow and blue and labeled with the
  corresponding time $t=2000$ and $t=9000$. The midplane curve is
  denoted as $C_M$. We see that the intermonolayer slip is largest
  for large shear rates.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Membrane Ruptures}

A pore formation or a complete membrane rupture can occur at large shear
rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture when
suspended in a shear flow with shear rate $\chi=0.1$. The streamlines
are included in these plots. An interesting phenomenon occurs in panels
(c) and (d) where two separated bilayers move along the background shear
flow symmetrically. Consequently, a periodic motion for bilayers may
occur at certain shear rates. One can expect that these two layers will
diverge from one another for much higher shear rates.

\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%\includegraphics[height=2in]{N58_rupt_0.pdf}
%\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
%\includegraphics[height=2in]{N58_rupt_400.pdf}
%\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Membrane rupture occurs when the shear rate
  exceeds a threshold. Here the shear rate is $\chi = 0.1$. Starting
  with a circular shape (panel (a)), the vesicle is stretched by the
  background flow and multiple pores form (panel (b)). Panels (c)--(d)
  show the later states during the simulation. Streamlines are included
  in each panel.}
\end{figure}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{\label{figure9} The shape and trajectories of two
  JP vesicles suspended in a shear flow. The moving paths of the two
  centroids are plotted in blue and red. The centroids are initially
  located on the $x$-axis. For simulation time, $t = {0, 400,800,1200}$
  for (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).
  The fluid velocity profile is plotted in the background.
  }
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{\label{figure11} Two JP vesicles suspended in
  an extensional flow. The moving paths of the two centroids are plotted
  in blue in red. Each row corresponds to a different initial placement
  of the JP vesicles. The flow rate is $\chi = 0.005$ in all cases.
  (i) Both JP vesicle centroids are on the $x$-axis. (ii) The
  centroid of the left JP vesicle is $0.1$ units above the $x$-axis
  and the right JP vesicle is on the $x$-axis. (iii) The centroid of
  the left JP vesicle is $0.1$ units above the $x$-axis and the right
  JP vesicle is $0.1$ units below the $x$-axis. (iv) The centroid of
  the left JP vesicle is $0.5$ units above the $x$-axis and the
  centroid of the right JP vesicle is $0.5$ units below the $x$-axis.
  Figure~\ref{figure12} presents the numerical results from the case
  (iii).  The fluid velocity profile is plotted in the background.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=11.5cm]{Figure3_Wrapper.pdf}
%\includegraphics[width=0.3\textwidth]{N58_0.pdf}
%\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
%\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
%\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{\label{figure3} A JP vesicle suspended in a shear flow with
  shear rate $\chi=0.0025$. (a) The initial configuration of a 58-body
  JP vesicle where the black arrows point in the direction of the
  hydrophobic side of the JP. (b) The particle velocities and
  streamlines of the configuration in (a). The streamlines are plotted
  in the background as solid curves and the red arrows represent the
  particle velocities. (c) The deformed tank-treading JP vesicle at
  $t=4000$. (d) The particle velocities and streamlines of the
  configuration in (c). The background colors in panels (a) and (c)
  represent the strength of the hydrophobic attraction potential. The
  blue regions have the weakest action and the red regions in the
  bilayer have the strongest action.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tank-Treading Vesicles}
\begin{figure}
\begin{center}
\includegraphics[width=13.5cm]{Figure4_Wrapper.pdf}
%\hspace{-0.6cm}
%\includegraphics[height=2in]{ReducedArea.pdf}
%\hspace{0.6cm}
%\includegraphics[height=2in]{DecayRate.eps}\\
%\includegraphics[height=2in]{ArcLength.pdf}
%\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{\label{figure4} (a) The reduced area transitioning over time
  for four different shear rates. The smooth curves are a best-fit
  exponential curve. (b) The decay rate $k$, using the exponential fit
  to the data in panel (a), for a number of shear rates. The inset shows
  the terminal reduced areas. (c) The total arc lengths of the midplanes
  over time for four shear rates. (d) The excess length of the
  midplanes. For all panels, a set of shear rates
  $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. The
  legend in panel (d) applies to both panels (a) and (c).}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
Our hydrodynamic simulation studies begin by studying the dynamics of a single JP vesicle suspended in
the shear flow
\begin{align}
  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
\end{align}
with shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
and $\mathbf{e}_y$ for the horizontal and vertical directions,
respectively. It is well known that a vesicle has tank-treading behavior
when there is no viscosity contrast between the fluids inside and
outside of the vesicle.
%Within the framework of the simulation setup,
%the proposed model provides a feature that the fluid viscosity is
%constant over the computational domain and it is capable of performing
%these simulations.

\begin{figure}
\begin{center}
\includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
\includegraphics[width=11cm]{Figure5B_Wrapper.pdf}
%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
%\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} The schematic of the inter-monolayer slip over
  time. Taking a shear rate $\chi=0.005$ as an example, we denote the
  mean angle between each particle pair $\theta(t)$ where the angle is
  calculated from the relative position of the particles with respect to
  the JP vesicle's center of mass. The configuration plots have two
  fixed particles marked in yellow and blue and labeled with the
  corresponding time $t=2000$ and $t=9000$. The midplane curve is
  denoted as $C_M$. We see that the inter-monolayer slip is largest
  for large shear rates.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Inter-Monolayer Friction}

The granulated JP vesicle allows us to consider inter-monolayer slip
between the two leaflets. When the shear rate is sufficiently large,
take $\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip
between a pair of particles over time. The pair we consider are colored
in blue and yellow. In this series of tests, we compute the mean
particle position and mean angle $\theta(t)$ between the particle
relative positions with respect to the vesicle center. It is clear that
the outer leaflet has larger tangential velocity than the inner leaflet
since $\theta(t)$ increases. This inter-leaflet sliding phenomenon is
consistent with what has been seen in articles in molecular dynamics
simulations. (\cite{Zgorski2019,denOtter2007})

\subsubsection{Membrane Ruptures}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%\includegraphics[height=2in]{N58_rupt_0.pdf}
%\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
%\includegraphics[height=2in]{N58_rupt_400.pdf}
%\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Membrane rupture occurs when the shear rate
  exceeds a threshold. Here the shear rate is $\chi = 0.1$. Starting
  with a circular shape (panel (a)), the vesicle is stretched by the
  background flow and multiple pores form (panel (b)). Panels (c)--(d)
  show the later states during the simulation. Streamlines are included
  in each panel.}
\end{figure}
A pore formation or a complete membrane rupture can occur at large shear
rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture when
suspended in a shear flow with shear rate $\chi=0.1$. The streamlines
are included in these plots. An interesting phenomenon occurs in panels
(c) and (d) where two separated bilayers move along the background shear
flow symmetrically. Consequently, a periodic motion for bilayers may
occur at certain shear rates. One can expect that these two layers will
diverge from one another for much higher shear rates.

\subsection{Self-Assembly and Relaxation}

@@

\subsection{Stretching and Permeability}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure1_Wrapper.pdf}
%\includegraphics[height=2in]{relax2.eps}
%\includegraphics[height=2in]{relax.eps}\\
%\includegraphics[height=2.in]{N58_0pres.pdf}
%\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
\caption{\label{figure2} A JP Vesicle relaxing under a quiescent flow.
  (a) The blue dashed and solid curves are mean magnitudes of the
  particle velocities in $x$ and $y$ directions, respectively. The red
  curve shows the decreasing trend of the mean magnitude of particle
  orientation change. The black dashed line shows the reference of how
  all magnitudes decay. (b) Bilayer configurations for $t=0$ (black) and
  $t=1000$ (red) with particle directors. (c)--(d) show the fluid
  pressure profiles for $t=0$ and $t=1000$ where the background curves
  indicate the streamlines. In panel (c), the pressure value in internal
  fluid is much higher than the pressure outside of the bilayer. After
  the JP vesicle relaxes, this immersed permeable bilayer approaches the
  steady state shown in panel (d).}
\end{figure}
Figures~\ref{figure2}c and~\ref{figure2}d demonstrate that the initial, non-equilibrium configuration has a large internal fluid pressure
that vanishes as the configuration tends toward the equilibrium state.  
This suggests that the initial collection of JP is under tension and
this tension is relaxed as fluid is expelled through the inter-particle
spacing. To make a comparison with membrane continuum mechanics, lipid
bilayer membranes have a large area modulus $K_A$ of about $240$ pN
nm$^{-1}$ \cite{NAGLE} and changes in surface area give rise to a
membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
membrane surface area and $A_0$ is the reference surface area in the
non-tensed state. In the two-dimensional vesicles, the tension becomes
\begin{align}
\label{eq:stretch}
\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
\end{align}
where $L$ and $L_0$ are the vesicle arc length and resting length,
respectively. A stretched, circular vesicles has a Laplace pressure 
\begin{align}
\label{eq:LaplacePressure}
\Delta p = \frac{\tilde \gamma}{R},
\end{align}
where $\Delta p$ is the difference in internal pressure to the pressure
at infinity and $R$ is the radius of the circular vesicle. The factor
$R^{-1}$ is the total curvature since the principle curvature in the
direction of the cylinder is zero.

@@

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure9_Wrapper.pdf}
%  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{\label{figure9} The shape and trajectories of two
  JP vesicles suspended in a shear flow. The moving paths of the two
  centroids are plotted in blue and red. The centroids are initially
  located on the $x$-axis. For simulation time, $t = {0, 400,800,1200}$
  for (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).
  The fluid velocity profile is plotted in the background.
  }
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.97\textwidth]{Figure11_Wrapper.pdf}
%\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{\label{figure11} Two JP vesicles suspended in
  an extensional flow. The moving paths of the two centroids are plotted
  in blue in red. Each row corresponds to a different initial placement
  of the JP vesicles. The flow rate is $\chi = 0.005$ in all cases.
  (i) Both JP vesicle centroids are on the $x$-axis. (ii) The
  centroid of the left JP vesicle is $0.1$ units above the $x$-axis
  and the right JP vesicle is on the $x$-axis. (iii) The centroid of
  the left JP vesicle is $0.1$ units above the $x$-axis and the right
  JP vesicle is $0.1$ units below the $x$-axis. (iv) The centroid of
  the left JP vesicle is $0.5$ units above the $x$-axis and the
  centroid of the right JP vesicle is $0.5$ units below the $x$-axis.
  Figure~\ref{figure12} presents the numerical results from the case
  (iii).  The fluid velocity profile is plotted in the background.}
\end{figure}
